Manuscript

### 2015-05-17 inst/wtc-finland/manuscript2.Rmd
...

# Elevation model data: http://www.eea.europa.eu/data-and-maps/data/digital-elevation-model-of-europe
elevation <- raster(file.path(context$rawDataDirectory, "elevation1x1_new.tif"))
r <- raster::crop(elevation, extent(elevation, 200, 1500, 2600, 3500))
raster::projection(r) <- "+proj=laea +lat_0=52 +lon_0=20 +x_0=5071000 +y_0=3210000 +a=6378137 +b=6378137 +units=m +no_defs"
elevation <- raster::projectRaster(r, crs="+init=epsg:2393")
r <- raster::crop(elevation, extent(3400000, 3410000, 7000000, 7010000) * 10)
s <- raster(extent(3355003, 3455003, 6955246, 7055246), 100, 100, crs="+proj=laea +lat_0=52 +lon_0=20 +x_0=5071000 +y_0=3210000 +a=6378137 +b=6378137 +units=m +no_defs")
r <- raster::resample(r, s) # Changing projection does not work perfectly. Has to resample to fix.
r1 <- as.data.frame(rasterToPoints(r))
colnames(r1) <- c("x","y","value")
coords <- raster::xyFromCell(r, cell=1:ncell(r))
x <- smoothSubsets(r=r, coords=coords, kernelFun=expKernel, scales=c(2000), .parallel=T)

>>>>

# Elevation model data: http://www.eea.europa.eu/data-and-maps/data/digital-elevation-model-of-europe
elevation <- raster(file.path(context$rawDataDirectory, "elevation1x1_new.tif"))
r <- raster::crop(elevation, extent(elevation, 200, 1500, 2600, 3500))
raster::projection(r) <- "+proj=laea +lat_0=52 +lon_0=20 +x_0=5071000 +y_0=3210000 +a=6378137 +b=6378137 +units=m +no_defs"
elevation <- raster::projectRaster(r, crs="+init=epsg:2393")
r <- raster::crop(elevation, extent(3400000, 3410000, 7000000, 7010000) * 10)
s <- raster(extent(3355003, 3455003, 6955246, 7055246), 100, 100, crs="+proj=laea +lat_0=52 +lon_0=20 +x_0=5071000 +y_0=3210000 +a=6378137 +b=6378137 +units=m +no_defs")
r <- raster::resample(r, s) # Changing projection does not work good enough. Have to resample to fix.
r1 <- as.data.frame(rasterToPoints(r))
colnames(r1) <- c("x","y","value")
coords <- raster::xyFromCell(r, cell=1:ncell(r))
x <- smoothSubsets(r=r, coords=coords, kernelFun=expKernel, scales=c(2000), .parallel=T)
